% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}      

Such a journey, and it's already ending. This thesis is a clean example that research - and science in general - is a social activity. Far from isolated ivory towers, very little would have been possible without the exceptional contribution of colleagues and friends, and without the constant support of those close to me. I owe you all my deepest gratitude!\\

First, I would like to thank my principal supervisor Jorge Gonçalves for his attentive guidance, his witty remarks and the intellectual flexibility he allowed me: coming from a control engineer, this was a double bliss! Many thanks to my co-supervisors Alex(ander) Skupin and Peter Ashwin: you gave me so many opportunities to grow as a researcher that I cannot count - projects, insights, travels. A special thank to Rudi Balling, the former director of the LCSB, for having created such a multidisciplinary and stimulating environment. Another special thank to Stefano Magni, almost an adjoint supervisor, to Johan Markdhal, bringing amoebas to other dimensions, to Françoise Kemp, a great partner in crime, and to Andreas Husch, who believed in a little physicist and suggested so many working challenges.

A big thank to my colleagues, I really enjoyed working with you. Thanks to whom I managed to collaborate with and to the others, always keen to share an idea, an insight, a cup of tea: Arthur, Atte, Beatriz, François, Gustavo, Jan, Jesùs, Laurent, Maria, Marino, Matias, Mehri, Mila, René, Vladimir, Xin. Thanks to all members of other amazing groups: the CriTiCS DTU first and foremost, the ResearchLuxembourg COVID-19 taskforce WP6, the ICS group, the RSG Luxembourg, the dynamical group in Exeter, Matti from cold Finland. There are many other people, in and outside the LCSB, that made this journey unforgettable; you know you'll be stalked for extra projects and ideas!

Thanks to Sofia, Laurence, Sabine and all the secretaries, communication team and staff. Much wouldn't have been possible without your reliable support. \\

Thanks to my friends, old and new: you have been a mind-easing presence.

Thanks to my family, always interested, cheering and motivating. Without you, I wouldn't be what I am - for that, I am truly grateful.

And thanks to Chiara: you've been everything. \\

So long, and thanks for all the fish.

\end{acknowledgements}
